Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-02-20 paper/paper.tex
update table 3

\begin{table}[h!]
  \small
  \caption{\label{table:results}Results.}
  \centering
  \begin{tabular}{lrrp{9cm}}
    \toprule
    \multicolumn{1}{c}{Name} &
    \multicolumn{1}{c}{\#~Rules created} &
    \multicolumn{1}{c}{Rank} \\
    \midrule
    Ping Scan & - & - \\
    SYN Flood & - & - \\
    JBoss JMX & 283 & 19 \\
    WeBid & - & - \\    
    ColdFusion & 566 & 37 \\
    .htaccess access & 572 & 1 \\
    .idq access & 700 & 136 \\
    iisadmin access & 502 & 117 \\
    /system32/ in URI & 1,060 & 191 \\
    Script tag in URI & 1,332 & 304 \\
    \bottomrule
  \end{tabular}
\end{table}

\begin{table}[h!]
  \small
  \caption{\label{table:weight}Weight Combinations.}
  \centering
  \begin{tabular}{lrrp{15cm}}
    \toprule
    \multicolumn{1}{c}{Name} &
    \multicolumn{1}{c}{Weights} &
    \multicolumn{1}{c}{Rank} \\
    \midrule
    Ping Scan & - & - \\
    SYN Flood & - & - \\
    JBoss JMX & 1,0,1,1 & 107 \\
    WeBid & - & - \\    
    ColdFusion & 0,1,1,1 & 7 \\
    .htaccess access & 0,1,1,1 & 11 \\
    .idq access & 0,1,1,1 & 7 \\
    iisadmin access & 0,1,1,1 & 2 \\
    /system32/ in URI & 0,1,1,1 & 11 \\
    Script tag in URI & 0,1,1,1 & 9 \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\begin{table}[h!]
  \small
  \caption{\label{table:results}Results.}
  \centering
  \begin{tabular}{lrrrp{9cm}}
    \toprule
    \multicolumn{1}{c}{Name} &
    \multicolumn{1}{c}{\#~Rules created} &
    \multicolumn{1}{c}{Rank} &
    \multicolumn{1}{c}{Rank fitness global} \\
    \midrule
    Ping Scan & - & - & - \\
    SYN Flood & - & - & - \\
    JBoss JMX & 382 & 208 & 23 \\
    WeBid & - & - & - \\    
    ColdFusion & 34 & 5 & 5\\
    .htaccess access & 2107 & 365 & 2\\
    .idq access & 1112 & 429 & 2 \\
    iisadmin access & 862 & 372 & 1 \\
    /system32/ in URI & - & - & - \\
    Script tag in URI & - & - & - \\
    \bottomrule
  \end{tabular}
\end{table}

%%\begin{table}[h!]
%%  \small
%%  \caption{\label{table:weight}Weight Combinations.}
%%  \centering
%%  \begin{tabular}{lrrp{15cm}}
%%    \toprule
%%    \multicolumn{1}{c}{Name} &
%%    \multicolumn{1}{c}{Weights} &
%%    \multicolumn{1}{c}{Rank} \\
%%    \midrule
%%    Ping Scan & - & - \\
%%    SYN Flood & - & - \\
%%    JBoss JMX & 1,0,1,1 & 107 \\
%%    WeBid & - & - \\    
%%    ColdFusion & 0,1,1,1 & 7 \\
%%    .htaccess access & 0,1,1,1 & 11 \\
%%    .idq access & 0,1,1,1 & 7 \\
%%    iisadmin access & 0,1,1,1 & 2 \\
%%    /system32/ in URI & 0,1,1,1 & 11 \\
%%    Script tag in URI & 0,1,1,1 & 9 \\
%%    \bottomrule
%%  \end{tabular}
%%\end{table}
%%
